More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-01-24 2016-Weak-FH-Bisim/WeakBisim.tex
small sentence over skype

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. We also consider for the third case $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$. So we have: \\ 
$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
and
$ Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\

>>>>

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l$. So we have: \\ 
$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
and
$ Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\
